Transactions Fraud Detection using Machine Learning and Nature Inspired Algorithms

### 2020-05-30 paper/main.tex
Reformat figures and tables

\begin{table}[]
	\begin{center}
		\begin{tabular}{|l|rrrrr|}
			\hline
			\textbf{Population size \textbackslash Score} & \multicolumn{1}{l}{\textbf{FA}} & \multicolumn{1}{l}{\textbf{CS}} & \multicolumn{1}{l}{\textbf{BA}} & \multicolumn{1}{l}{\textbf{FPA}} & \multicolumn{1}{l|}{\textbf{GWO}} \\ \hline
			\textbf{10}                                             & 0.753                           & \textbf{0.752}                           & 0.759                           & 0.754                            & 0.776                             \\
			\textbf{20}                                             & 0.757                           & 0.746                           & 0.755                           & 0.750                            & 0.771                             \\
			\textbf{50}                                             & \textbf{0.761}                           & 0.751                           & \textbf{0.761}                           & \textbf{0.756}                            & \textbf{0.782}                             \\ \hline
		\end{tabular}
	\end{center}
	\begin{center}
		\caption{Highest train scores (ROC AUC) of nature inspired algorithms by population size. We may notice that Grey Wolf Algorithm (GWO) outperformed all of the other algorithms.} \label{tab:nia_comparison}
	\end{center}
\end{table}

@@

\begin{table}[]
	\begin{center}
		\begin{tabular}{|lrrr|}
			\hline
			\textbf{Feature selection type} & \textbf{Train score} & \textbf{Test score} & \textbf{Selected features} \\ \hline
			All features                    & N/A                  & 0.713               & 240                                  \\
			Recursive feature elimination   & 0.747                & 0.719               & 112                                  \\
			Firefly Algorithm               & 0.761                & 0.663               & 114                                  \\
			Cuckoo Search                   & 0.753                & 0.718               & 106                                  \\
			Bat Algorithm                   & 0.761                & 0.689               & 125                                  \\
			Flower Pollination Algorithm    & 0.756                & 0.706               & 113                                  \\
			\textbf{Grey Wolf Optimizer}             & \textbf{0.782}                & \textbf{0.733}               & \textbf{53}                                   \\ \hline
		\end{tabular}
	\end{center}
	\begin{center}
		\caption{Comparison of the baseline models with nature-inspired algorithms. The train score stands for the best score from the optimization. All of the nature-inspired algorithms (except Grey Wolf Optimizer) achieved a better train score than recursive feature elimination, however, they overfit the model which resulted in a worse test scores.} \label{tab:nia_baseline_comparison}
	\end{center}
\end{table}

\begin{figure}[ht]
	\begin{center}
	    \includegraphics[width=5.5cm]{figures/nia_selected_features_by_algorithm.png}
    \end{center}
	\caption{Number of selected features by algorithm - Grey Wolf Algorithm selected by far the least number of features.}
	\label{fig:nia_selected_features_by_algorithm}
\end{figure}

>>>>

\def\arraystretch{1.5}
\begin{table}[]
	\begin{center}
		\begin{tabular}{|l|r|r|r|r|r|}
			\hline
			\textbf{Population size \textbackslash Score} & \multicolumn{1}{l|}{\textbf{FA}} & \multicolumn{1}{l|}{\textbf{CS}} & \multicolumn{1}{l|}{\textbf{BA}} & \multicolumn{1}{l|}{\textbf{FPA}} & \multicolumn{1}{l|}{\textbf{GWO}} \\ \hline
			\textbf{10}                                             & 0.753                           & \textbf{0.752}                           & 0.759                           & 0.754                            & 0.776                             \\
			\textbf{20}                                             & 0.757                           & 0.746                           & 0.755                           & 0.750                            & 0.771                             \\
			\textbf{50}                                             & \textbf{0.761}                           & 0.751                           & \textbf{0.761}                           & \textbf{0.756}                            & \textbf{0.782}                             \\ \hline
		\end{tabular}
	\end{center}
	\begin{center}
		\caption{Highest train scores (ROC AUC) of nature inspired algorithms by population size. We may notice that Grey Wolf Algorithm (GWO) outperformed all of the other algorithms.} \label{tab:nia_comparison}
	\end{center}
\end{table}

@@

\begin{table}[]
	\begin{center}
		\begin{tabular}{|l|r|r|r|}
			\hline
			\textbf{Feature selection type} & \textbf{Train score} & \textbf{Test score} & \textbf{Selected features} \\ \hline
			All features                    & N/A                  & 0.713               & 240                                  \\
			Recursive feature elimination   & 0.747                & 0.719               & 112                                  \\
			Firefly Algorithm               & 0.761                & 0.663               & 114                                  \\
			Cuckoo Search                   & 0.753                & 0.718               & 106                                  \\
			Bat Algorithm                   & 0.761                & 0.689               & 125                                  \\
			Flower Pollination Algorithm    & 0.756                & 0.706               & 113                                  \\
			\textbf{Grey Wolf Optimizer}             & \textbf{0.782}                & \textbf{0.733}               & \textbf{53}                                   \\ \hline
		\end{tabular}
	\end{center}
	\begin{center}
		\caption{Comparison of the baseline models with nature-inspired algorithms. The train score stands for the best score from the optimization. All of the nature-inspired algorithms (except Grey Wolf Optimizer) achieved a better train score than recursive feature elimination, however, they overfit the model which resulted in a worse test scores.} \label{tab:nia_baseline_comparison}
	\end{center}
\end{table}

\begin{figure}[ht]
	\begin{center}
	    \includegraphics[width=7.5cm]{figures/nia_selected_features_by_algorithm.png}
    \end{center}
	\caption{Number of selected features by algorithm - Grey Wolf Algorithm selected by far the least number of features.}
	\label{fig:nia_selected_features_by_algorithm}
\end{figure}
